Analysis paper

### 2021-06-15 analysis/analysis.Rmd
update plots

```{r truth-vs-forecasts, fig.height=12, fig.width=15}
# create helper function for the plot ------------------------------------------
truth_and_pred_plot <- function(df, ttype = "case") {
  p <- df %>%
    dplyr::filter(target_type == ttype) %>%
    ggplot(aes(y = true_value, x = target_end_date)) + 
    geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
                   size = 1.7,
                   alpha = 1,
                   position = position_dodge(width = 4)) + 
    # geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
    #                size = 1.7,
    #                alpha = 0.1,
    #                position = position_dodge(width = 4)) +   
    geom_point(data = unfiltered_data[target_type == ttype], 
               aes(shape = classification)) + 
    geom_line(data = unfiltered_data[target_type == ttype]) + 
    theme_light() + 
    facet_wrap(~ location_target, scales = "free", ncol = 2) + 
    theme(legend.position = "bottom") + 
    # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 7, 
                            max(forecast_dates$full_hub_period)))
  return(p)
}

>>>>

```{r truth-vs-forecasts, fig.height=12, fig.width=15}
# create helper function for the plot ------------------------------------------
truth_and_pred_plot <- function(df, ttype = "case") {
  p <- df %>%
    dplyr::filter(target_type == ttype) %>%
    ggplot(aes(y = true_value, x = target_end_date)) + 
    geom_linerange(aes(ymin = `0.25`, ymax = `0.75`, color = model), 
                   size = 1.7,
                   alpha = 1,
                   position = position_dodge(width = 4)) + 
    # geom_linerange(aes(ymin = `0.025`, ymax = `0.975`, color = model), 
    #                size = 1.7,
    #                alpha = 0.1,
    #                position = position_dodge(width = 4)) +   
    geom_point(data = unfiltered_data[target_type == ttype], 
               aes(shape = classification)) + 
    geom_line(data = unfiltered_data[target_type == ttype]) + 
    theme_light() + 
    facet_wrap(~ location_target, scales = "free", ncol = 2) + 
    theme(legend.position = "bottom") + 
    # theme(panel.background = element_rect(fill = "#e1f0fe")) + 
    scale_x_date(limits = c(min(forecast_dates$full_hub_period) + 5, 
                            max(forecast_dates$full_hub_period)))
  return(p)
}
